---
title: "Lesson 15 HW"
author: "Joshua Susanto 405568250"
date: "5/27/2021"
output: html_document
---

I tried to make multiple functions for some problems for practice

# 1

## A
```{r}
h <- function(x) {
    vec <- c()
    for(i in 0:x) {
        y <- 3^i
        vec <- c(vec, y)
    }
    return(vec)
}

sum(h(5))
```

```{r}
vec <- c()
for(i in 0:5) {
  y <- 3^i
        vec <- c(vec, y)
        print(sum(vec))
}
```

```{r}
y = 0

for(i in 0:5){
  y <- 3^i + y
  if(i == 5){
print(y)
  }
}
```

## B
```{r}
i <- 0
b <- c()
while (i < 6) {
      a <- 3^i
      b <- c(b, a)
        i = i+1
}
sum(b)
```

```{r}
y = 0
i <- 0
while (i < 6) {
  y <- 3^i + y
  i = 1 + i
  if(i == 6){
print(y)
  }
}
```


## C
```{r}
sum(3^(0:5))
```

# 2
```{r}
x <- 6

for (i in 1:3) {
  if (x %% 3 == 0) {
    x <- x/3
  } else {
    x <- 3*x + 1
  }
}

```

## A

The first line sets the object x equal to 6. The second line utilizes a for loop for i from 1 through 3. Embedded within this first for loop is an if function with the condition that the remainder of x divided by 3 is equal to 0. In this case x is still 6 so x %% 3 is  0. This activates the condition and x is now divided by 3 and our new x value is 2. With our second loop (i = 2) we enter the if function again but with our x value equal to 2 now. 2 divided by three has a remainder and is thus not equal to 0. This activated the else function where we now compute the new x to be 7. We enter the loop for the final time (i = 3) with our new x being equal to 7. Checking the if condition again we find that 7 is also not divisible by 3 and the else loop is activated. We then finally compute x to be 3*7 + 1 which would make x finish as 22.

## B
```{r}
x <- 6

for (i in 1:3) {
  ifelse(x %% 3 == 0, x <- x/3, x <- 3*x +1) 
  x <- x
}

```

