---
title: "week5 discussion answers"
author: "Joshua Susanto"
date: "5/3/2021"
output: html_document
---

1. The dataset is called train.csv and the descriptions for each field are supplied in data_description.txt. Each row of data contains one home sale. Download and load the data.
```{r}
train <- read.csv("train.csv")
```

2. What is the average sale price for homes sold in Ames in 2006?
```{r}
train2 <- train[train$YrSold == 2006,]
mean(train2$SalePrice)
```

3. What is the median sale price for homes sold in 2006 which have an indoor square footage of greater than or equal to 2000 ft (excluding porches, garages, decks, and veneers)? What percentage of homes meet this criterion?
```{r}
train2$indoorSF <- train2$GrLivArea + train2$TotalBsmtSF
median(train2$SalePrice[train2$indoorSF >= 2000])
(length(train2$SalePrice[train2$indoorSF >= 2000])/length(train$Id))*100
```

Note: Challenge yourself! This is a slightly less demanding version of the actual question. In reality, you would have been given the additional task of calculating this metric by neigborhood – you should still be able to do this, but we haven’t learned about some of the more elegant ways to do this.

4. A client approaches you with a question about the local housing market. They’re interested in whether more homes are sold at certain times of year than others? In other words, is there seasonality? Provide a visualization and a brief description of your findings.
```{r}
train$MoSold<-as.numeric(train$MoSold)
OurPlot <- ggplot(train, aes(MoSold)) + 
  geom_histogram(aes(y = ..density.., fill = ..count..), bins=12, color = "#FFD100") + geom_density(alpha=0.4, color="gray")  + 
  facet_wrap(~YrSold, ncol=1) + 
  geom_hline(yintercept=0, colour="white", size=1) + 
  scale_fill_gradient("Count", low = "white", high = "#2774AE") + 
  scale_x_discrete(name ="Month", limits=c(
    "Jan","Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug","Sep","Oct", "Nov","Dec")) + 
  scale_y_continuous(labels=scales::percent_format()) + 
  labs(y= "Homes Sold", x = "Month") + 
  ggtitle("Distribution of Homes Sold") + 
  theme(panel.background = element_blank(), strip.text.x = element_text(size = 12, face = "bold"), 
        plot.title = element_text(size = 18, face = "bold", hjust = 0.5)) 
print(OurPlot)
```

Note: For the visualization, you were allowed to use R plots, Python’s matplotlib, Tableau, Excel charts, or whatever tool you like. Of course, we’ll use R!

5. You’re a contractor consulting for a client who wants to remodel their home and then sell it on the market. What factors may be important for them to consider in their remodel? Use a visualization to illustrate your choices.
```{r}
library(ggcorrplot)
ames.numeric <- na.omit(select_if(ames, is.numeric))
str(ames.numeric)
ames.cor<-cor(ames.numeric)  
OurPlot2<- ggcorrplot(ames.cor, type = "upper",
     outline.col = "white", colors = c("#FFD100", "white", "#2774AE")) + 
  ggtitle("Correlogram of Ames Numeric Data") + 
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust=0.5),axis.text.y = element_text(size = 8))
print(OurPlot2)
```

